Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-17 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

@@

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain kind of QIVPMs, we also want to understand
what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
This result will first be generalized in this section, and then we
will show some QIVPMs may not be induced by any quantum probability
measure, i.e., no state is consistent with these kind of QIVPMs, while
there is always an unique state consistent with a quantum probability
measure by Gleason's theorem.

@@

\begin{tabular}{cccc}
\toprule 
\addlinespace
\multicolumn{2}{c}{$\mathscr{I}_{n}$} & \multicolumn{2}{c}{$\mathscr{I}_{2}$}\tabularnewline\addlinespace
\midrule 
\addlinespace
$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
\textrm{for odd }k
\end{gathered}
$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\multirow{2}{*}{$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
\textrm{for even }k\\
0<k<2n
\end{gathered}
$} & \multirow{2}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
\cmidrule{3-4} 
\addlinespace
 &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Hence, given a real-valued probability~$x$, we could easily replace
it with an interval~$\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.

After we have the rule to replace a real number by an interval, any
Born rule probability~$\mu_{\rho}^{\mathrm{B}}$ on a three-dimensional
Hilbert space can be extended to a QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
where $\circ$ is the function concatenation~\citep{HOSTunpublished}.
For example, when $n=2$, two quantum probability measures~$\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\mu_{\rho_{0}}^{\mathrm{B}}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$
and $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$,
for any projector $P$ in the minimal subspace of events containing
$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, are computed
straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$ based on $\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\mu_{\rho_{0}}^{\mathrm{B}}$ on $\events_{C}$.}

\begin{tabular}{ccccc}
\toprule 
\addlinespace
$P$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Verifying $\iota_{2}\circ\mu_{1}$ and $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
are QIVPMs are also straightforward.

A state~$\rho$ is called totally mixed state if it satisfies $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
Given any totally mixed state~$\rho$, we know not only $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM, but also the collection of states consistent it get closer
and closer to $\rho$ as the intervals get narrower and narrower,
eventually collapsing to $\rho$ when the intervals become infinitely
precise real numbers. To state this result, we need to define a notion
of distance based on the following norm of a matrix~$A$ as $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$~\citep{544199}.
If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
its distance with $\rho$, $\left\Vert \rho-\rho'\right\Vert $, must
be bounded by $1/n$. Reversely, if the distance between $\rho$ and
$\rho'$ is bounded by $\left(12n\right)^{-1}$, then $\rho'$ is
consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$~\citep{HOSTunpublished}.
For example, $\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed
states. Since $\left\Vert \frac{\mathbb{1}}{3}-\rho_{0}\right\Vert \le\frac{1}{24}$,
we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$
and $\mathbb{1}/3\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
In general, as $n$ goes to infinity, only the states very close to
$\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$,
and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will become closer and closer to $\rho$.

In the limiting case when the intervals are infinitely precise, i.e.,
$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, even if a QIVPM is
not \emph{a priori} known to be induced by a state, it can be recast
as a real-valued one and will have a unique state consistent with
it on every projector. This fact is called Gleason's theorem.

\begin{thm}[Gleason~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, there exists a unique state~$\rho$
such that $\mu=\mu_{\rho}^{\mathrm{B}}$. \end{thm}

\noindent However, if the intervals are only with finite-precision,
there are some QIVPMs which cannot be consistent with any state. Given
a three-dimensional Hilbert space $\Hilb$ with an orthonormal basis
$\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and \begin{subequations} 
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations} It is straightforward to verify that $\bar{\mu}$
is a QIVPM. Then we will prove $\coreBorn\left(\bar{\mu},\events\right)$
is an empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
for any~$P$, the state~$\rho$ must satisfy: 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all $j$. However, the last equation never holds. Thus, there
is no state consistent with the QIVPM on all projectors~$P\in\events$,
so Gleason's theorem cannot be extended to general QIVPMs because
of this example.

>>>>

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem*{example*}{Example}

@@

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain kind of QIVPMs, we also want to understand
what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
This result will first be generalized in this section, and introduce
a finite-precision extension of the Born rule~\citep{peres1995quantum,544199,Jaeger2007}.
The Born rule is essential to compute the conventional quantum probability
because any quantum probability measure can be induced by the Born
rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
We then provide a finite precision variant of Gleason's theorem for
QIVPMs induced by the Born rule, but there are also some general QIVPMs
may not be induced by any quantum probability measure, i.e., no state
is consistent with these kind of QIVPMs.

@@

\begin{tabular}{cccc}
\toprule 
\addlinespace
\multicolumn{2}{c}{$\mathscr{I}_{n}$} & \multicolumn{2}{c}{$\mathscr{I}_{2}$}\tabularnewline\addlinespace
\midrule 
\addlinespace
$[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\imposs$ & $\imposs$ & $\imposs$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
\textrm{for odd }k
\end{gathered}
$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\multirow{2}{*}{$\begin{gathered}\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\\
\textrm{for even }k\\
0<k<2n
\end{gathered}
$} & \multirow{2}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
\cmidrule{3-4} 
\addlinespace
 &  & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\necess$ & $\necess$ & $\necess$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}

\yutsung{Not sure what is the best way embedding the condition for
$k$ in the table...}
\end{table}
Hence, given a real-valued probability~$x$, we could easily replace
it with an interval~$\iota_{n}\left(x\right)=[\ell,r]$ if $x\in\textrm{Int}\left([\ell,r]\right)$.

After we have the rule to replace a real number by an interval, we
can induce a QIVPM from a state according to the following theorem.

\begin{thm}[Finite-precision Extension of the Born rule~\citep{HOSTunpublished}]For
any state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM, where $\circ$ is the function concatenation.\end{thm}\yutsung{Do
we need to summarize the proof?}

\noindent For example, when $n=2$, two states~$\mathbb{1}/3$ and
$\rho_{0}$ can induce two QIVPMs~$\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$, where $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
and $\rho_{0}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$.
The interval-valued probability of the induced QIVPMs, $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$
and $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$,
for any projector $P$ in the minimal subspace of events containing
$\proj{0}$, $\proj{1}$, and $\proj{2}$, $\events_{C}$, are computed
straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$ based on $\mu_{\mathbb{1}/3}^{\mathrm{B}}$
and $\mu_{\rho_{0}}^{\mathrm{B}}$ on $\events_{C}$.}

\begin{tabular}{ccccc}
\toprule 
\addlinespace
$P$ & $\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\mathbb{1}/3}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}

In the limiting case when the intervals are infinitely precise, i.e.,
$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$
with its corresponding $\iota_{\infty}\left(x\right)=[x,x]$, we can
formulate Gleason's theorem in our framework.

\begin{thm}[$\mathscr{I}_{\infty}$ Variant of Gleason]\label{cor:Gleason's}In
a Hilbert space $\Hilb$ of dimension $d\geq3$, given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
the states consistent with it on every project, $\coreBorn\left(\bar{\mu},\events\right)$
has a unique element. \end{thm}

Our framework allows us to generalize the above theorem to QIVPMs
induced by the finite-precision extension of the Born rule~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
get closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers. To state this result, we introduce
a few technical notions. We call a state~$\rho$ a \emph{totally
mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $. We
also define a notion of distance between two states~$\rho$ and $\rho'$
as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
and the set of all states whose distance with $\rho$ is bounded by
$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.

\begin{thm}[Finite-precision Extension of Gleason~\citep{HOSTunpublished}]In
a Hilbert space $\Hilb$ of dimension $3$, given any totally mixed
state~$\rho$, 
\begin{equation}
B_{\frac{1}{12n}}\left(\rho\right)\subseteq\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)\subseteq B_{1/n}\left(\rho\right)\,.
\end{equation}
\end{thm}\yutsung{Do we need to summarize the proof?}

\noindent In another word, if a state~$\rho'$ is consistent with
$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$. Reversely,
if the distance between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$,
then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
For example, $\mathbb{1}/3$ and $\rho_{0}$ are both totally mixed
states. Since $\left\Vert \frac{\mathbb{1}}{3}-\rho_{0}\right\Vert \le\frac{1}{24}$,
we should have $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$
and $\mathbb{1}/3\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
In general, as $n$ goes to infinity, only the states very close to
$\rho$ is guarantied belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\mathbb{1}/3}^{\mathrm{B}},\events\right)$,
and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will become closer and closer to $\rho$.

If a QIVPM is not \emph{a priori} known to be induced by a state,
there are some QIVPMs which cannot be consistent with any state.

\begin{example*}Given a three-dimensional Hilbert space $\Hilb$
with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
let $\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and \begin{subequations} 
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations} It is straightforward to verify that $\bar{\mu}$
is a QIVPM. Then we will prove $\coreBorn\left(\bar{\mu},\events\right)$
is an empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
for any~$P$, the state~$\rho$ must satisfy: 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all $j$. However, the last equation never holds. Thus, there
is no state consistent with the QIVPM on all projectors~$P\in\events$,
so Gleason's theorem cannot be extended to general QIVPMs because
of this example.\end{example*}
